\section{On the Description of Individuals}
\emph{Chronological ID:} \texttt{2024-01-07:01}

\emph{Structural ID:} \texttt{1.1.1}

There is a clear division between a fictional story, which primarily describes individuals and their psychologies, and to a lesser extent locations, and a worldbuilding document, which primarily describes larger-scale elements, no smaller than a single culture or a single language, and potentially as large as an entire galaxy. This treatise establishes its identity as a worldbuilding document, and makes no attempt to appeal to those who like fictional stories, as the author does not believe that ``worldstate literature'' could gain a broad appeal among humans.

That being said, the need to describe individuals might nevertheless arise. Some of those individuals are significant to the world that they live in, for various reasons. One of them might be that they influence the way society operates, as is the case with scientists, inventors and famous thinkers. Another might be that they controlled a large amount of the society's assets at some point, as is the case with politicians and enterpreneurs, as well as their pre-modern counterparts, that are usually called ``kings'' in pre-modern literature.

Whatever the case for an individual's fame within the Madelineverse is, a biography of them within the treatise adheres to strict requirements. It only mentions the individual's personal life details very briefly, often limiting itself to the individual's birth and death dates, and only including details which led to the individual creating or acquiring something that made them famous. This, for example, means that an individual's relatives, such as parents and children, are only relevant, and therefore described, if the position that the individual occupies is hereditary, like a monarchy or a family business.

However, people not significant to the world might also need descriptions, if they are the main or supporting characters of any fictional story set within the world. Such descriptions, however, are to be compiled into their own document, separate from this treatise, which will not start publishing until a fictional story set in the Madelineverse does. They are also not likely to use {\LaTeX} as a format, as much more suitable formats, such as MediaWiki, exist.
\newpage
