\section{On Ethical Use of AI in Creative Writing}
\emph{Chronological ID:} \texttt{2024-01-03:01}

\emph{Structural ID:} \texttt{1.2}

The technology of artificial intelligence, especially with regard to natural language generation and image generation, has made considerable advances in the recent years, with major players including OpenAI's ChatGPT and DALL\textperiodcentered{E}~3. If developed further, AI could become a significant boon to solo creators, allowing them to automate the creation and full illustration of worlds like the Madelineverse. However, AI as of the writing of this page raises numerous concerns, regarding both the state of the technology and its ethical usage.

The author makes the following observations from other users' interaction with ChatGPT and similar AI products:

\begin{itemize}
  \item The current AI technology largely fails at tasks requiring lots of novel thought, as would be the case, for example, in conlanging, where each vocabulary item has to be a string of characters likely never seen before in context. Therefore, automation of vocabulary creation, among other tasks, is still believed to be infeasible in the present day.
  \item AI may be classified as a creator, in and of its own right, just as a human would, though legislation has not been updated to reflect the fact as of yet, taking the United States as an example. Therefore, not disclosing which elements of a treatise like this one were written by AI would be unethical, no matter how minute the AI contribution is.
  \item AI tools generating images have often been criticised for being able to clone a specific artist's signature style, and therefore, supplant the need for the artist in question to be commissioned, depriving them of their income. As this treatise would benefit from a consistent art style, this is an inevitable concern if multiple illustrations are procured.
\end{itemize}

Despite all these concerns, however, the author does not feel the need to outright ban AI from any creative process in the Madelineverse. Currently, AI has not been used to produce any page, but any use of AI in the future will be clearly noted.
\newpage
