\section{Standard for Celestial Fact Sheets Describing Night Sky Stars}
\emph{Chronological ID:} \texttt{2024-01-31:01}

\emph{Structural ID:} \texttt{1.4.1.3}

Many tools created to aid worldbuilding projects, such as Artifexian's WorldSmith and SpaceEngine, allow for easy generation of stars within a certain distance of the ``home'' star or stars. This is appropriate for worldbuilding projects in which space travel is an available technology; however, it obviously nonsensical for those in which it is not, such as the Madelineverse. Instead, the treatise opts to describe the stars visible in the home planet's night sky, from brightest to dimmest.

Stars in the night sky require even less data than your typical minor planet to adequately describe, and therefore, a single page could potentially describe 20 stars. Only the following are deemed essential:

\begin{itemize}
  \item right ascension, declination, apparent magnitude, parallax, spectral class
\end{itemize}

Like with minor planets, a standard of precision is enforced, so that no single star is accidentally ``overdescribed'' when it could potentially be less important in-universe. The precision required is as follows:

\begin{itemize}
  \item \textsc{Right ascension:} 0.01 seconds (\$\$h\$\$m\$\$.\$\$s)
  \item \textsc{Declination:} 0.1 arcseconds (±\$\$$\degree$\$\$\textquotesingle\$\$.\$\textquotesingle\textquotesingle)
  \item \textsc{Apparent magnitude:} 0.01
  \item \textsc{Parallax:} 0.1 milliarcseconds
  \item \textsc{Spectral class:} 0.1 (X\$.\$X)
\end{itemize}

The task of generating the night sky stars is intended to be fully automated. However, the complementary task of devising constellations based on the night sky stars, as well as their cultural, mythological, etc. significance, is intended to be manual, once a detailed enough star chart can be drawn.
\newpage
