\section{Aesthetic vs Pragmatic Decisions}
\emph{Chronological ID:} \texttt{2024-01-04:01}

\emph{Structural ID:} \texttt{1.3}

Precursors to the Madelineverse cannot be said to have been ``designed''; rather, they grew organically out of a set of stories by two different authors. Those stories, while taking place in the same universe, had no underlying worldbuilding rules and vastly different goals in terms of storytelling and audience engagement, even when considering the work of one of the authors in isolation. However, common patterns in both certain groupings of stories and the world as a whole allowed an attentive observer to spot an emergent cohesive aesthetic, that could then be applied to any future work of fiction or worldbuilding project.

The Madelineverse has been designed as a ``perfect escape''; a world wherein most inhabitants are neither mostly occupied with nor stressed out by the duties required to contribute to a society, and therefore, are able to pursue self-actualisation in terms of creative or otherwise therapeutic activities. To this end, the society in question is very uniform, maintaining no political entities and only a single language throughout a period comparable to 2000 years on Earth.

That being said, with regard to a potential story set in the Madelineverse, a potential conflict is introduced. A character, originally severely lacking in self-reflection and only ever doing what society expects of her, finds herself at the core of major societal changes that disrupt the status quo, introducing a world with warring political entities and general distrust, and has to consider whether self-actualisation is a goal that actually matters anymore. These events, however, are only set to occur after the ``present day'' of Madelineverse worldbuilding, and are not reflected at all in this or any future treatises.

However, some elements of Madelineverse worldbuilding have been approached primarily from a worldbuilding-only perspective. The presence of a single dominant language, for example, is so that the majority of conlanging work can be done on that particular language and its evolutionary stages, rather than any sister or areal language. However, this is also understood to be unrealistic under normal circumstances, which further complements the worldbuilding by requiring special circumstances to be introduced.
\newpage
