\section{Maths and Science Skills of Computers}
\emph{Chronological ID:} \texttt{2023-01-06:01}

\emph{Structural ID:} \texttt{1.2.2}

The question of whether to use computer tools for a document that is, for both its core and its fine details, dependent on scientific and mathematical accuracy, surprisingly enough, one that does not solely rely on ethics. In the author's belief, the day when AI can be unquestionably trusted for a wide variety of topics is not yet on the horizon. Nevertheless, the current strengths of AI tools, as well as those that qualify as advanced calculators, for scientific engagement, are outlined here.

ChatGPT is a tool primarily created to make inferences on its own based on a large corpus of text, and has not been able to make many relevant inferences with regard to mathematics. Therefore, any mathematical output, even that as simple as the sum of two numbers, might be completely wrong. Certain aspects of worldbuilding, especially when well-known laws of physics are involved, require precise maths, which has to be done by hand or with calculators at this point in time, and any incorrect assumptions made by AI must be corrected before a page is published.

Wolfram$\vert$Alpha is a tool, significantly predating modern AI tools, that nevertheless attempts natural language processing to some degree, interpreting the user's input successfully as belonging to one of many scientific fields, including astrophysics. Therefore, it is an invaluable tool complementing ``simple'' formulas for stellar luminosity, composition and evolution, to say nothing of its capabilities in unit conversion and other simpler uses. However, as a tool intended for all sciences, it may be lacking in specialised fields.

One last-ditch effort that remains, however, is coding a specialised calculator, one that might require to do numerical integration or other non-intuitively implemented calculation, by hand in a general-purpose programming language. Some calculators belonging to this category, such as Universe Sandbox, already exist and can be used to further assist Madelineverse worldbuilding. However, the author does not rule out the possibility of a tool being coded specifically for the Madelineverse.
\newpage
