\section{World History: Broad Overview}
\emph{Chronological ID:} \texttt{2024-06-01:01}

\emph{Structural ID:} \texttt{4.2}

There is a year 0 placed between the Anno Fandomi years, counting forwards, and the Before the Sights years, counting backwards, for ease of application of the leap year rule and calculation of ages around the year. However, the adjustment of the leap year rule also slightly adjusted the position of year 0.

Historiography of the *Earth, due to the prevalence of the global trade network, is largely influenced by macroeconomic theories, and therefore admits periods of time known as ``revolutions'', ``recessions'' and ``periods of stability''. The known periods to modern historiographers are as follows:

\begin{itemize}
  \item The Agricultural Revolution (retroactive name, no contemporary name) (ca. 10,000-7500 BS)
  \item The Prehistoric Period of Stability (retroactive name, no contemporary name) (ca. 7500-3000 BS)
  \item The Historiographic Revolution (retroactive name, no contemporary name) (ca. 3000-2500 BS)
  \item The Pre-Global Period of Stability (retroactive name, no contemporary name) (ca. 2500-100 BS)
  \item The Educational Revolution (ca. 100 BS to year 0)
  \item The Calendar Revolution (ca. year 0 to 100 AF)
  \item The Pandemic Recession (ca. 100-200 AF)
  \item The Antique Period of Stability (retroactive name, contemporarily simply ``The Period of Stability'') (ca. 200-400 AF)
  \item The Fiat Money Revolution (ca. 400-500 AF)
  \item The Inflationary Recession (ca. 500-550 AF)
\end{itemize}

This list will be continued in page \texttt{4.2.1}.
\newpage
