\section{The Broad About}
\emph{Chronological ID:} \texttt{2024-01-01:01}

\emph{Structural ID:} \texttt{1}

The \textsc{Madelineverse} is a fictional universe created by \textsc{CreativityTheEmotion}, who may, on occasion, adopt the alias ``\textsc{Madeline Lovesick}'' for the purposes of the universe in question and no others. The universe is designed to have certain elements familiar to humans, such as a planet hosting a civilisation, that are meant to be conducive to a fictional story set within the universe. However, the main purpose of the creation of the Madelineverse is not to be support or background material for any fictional story, by the same author or otherwise.

In lieu of a fictional story, this treatise is intended to serve as both the primary documentation of the Madelineverse and the primary ``consumable'' for anyone wishing to learn about it. To that end, it is designed to consist of brief ``updates'', no more extensive than a single B5 page, each of which adds something small but significant to the compendium of Madelineverse knowledge. These updates may be read either in chronological order, by date of publishing, or in structural order, with related pages (e.g. everything about the in-universe languages) forming a single section.

The scope of Madelineverse worldbuilding is, in most concise possible terms, a single planet; the civilisation that the planet hosts has not developed space technology as of the ``present day'' of the setting. However, where needed, larger-scale elements, such as the planetary system that the planet is within, will be described, and in many cases, focusing on smaller-scale elements, such as a single city, will be necessary so as to not introduce extraneous detail.

Often, comprehensible world description, a requirement for adequate worldbuilding, is not possible without naming the elements of the world, such as peoples and cultures. However, there is often the innate desire to name the peoples and cultures in question by using the in-universe languages, which, themselves, are among the elements to be named, leading to a chicken-and-egg situation. Therefore, a ``necessary evil'' of the worldbuilding and its documentation is using temporary names for the elements until in-universe names can be generated, and then, retconning existing pages to replace the temporary names.
\newpage
