\section{Highlighting the Ethics of AI Tool Production}
\emph{Chronological ID:} \texttt{2024-01-05:01}

\emph{Structural ID:} \texttt{1.2.1}

Further concerns with use of AI for the production of Madelineverse content are raised here. They primarily concern the methods by which the AI tools used have been produced, which have been considered unethical and even possibly illegal by some, on multiple accounts. However, the concerns do not affect the conclusion reached in section \texttt{1.2}, as the author continues to believe that the ethics of use of current AI technology to produce content are unaffected by the ethics of the technology's production.

\begin{itemize}
  \item Most AI tools rely on a process called ``training'', in which a large corpus of material, similar to the material that the creators of the AI want it to generate, is fed to the AI in order to adjust its internal variables. In most cases, this material is copyrighted and the copyright owners do not consent to their work being used in such a way. The author, however, treats this as no different than the case of a human novel writer who honed their craft by reading a lot of copyrighted books, or a human visual artist who honed their craft by using a lot of copyrighted images as references, who would need to do so anyway if their specialisation was fanart.
  \item ChatGPT in particular also relies on a process officially called ``reinforcement learning from human feedback'' (RLHF), in which the output of the AI is deliberately adjusted so that it does not become complicit in aiding the user with illegal or unethical activities. However, the nature of RLHF has been highlighted by certain sources as relying on low-skill workers to chat with ChatGPT, often being exposed to disturbing graphic descriptions of activities that were being targeted, for minimum wage, outsourced to countries where the minimum wage is even lower than in the United States. The author believes this to be more of an issue of living wages and ethical work conditions for low-skill workers across the world, applicable to any industry, rather than that particular to AI, and does not feel the need to refrain from using an unethically produced product when an ethically produced alternative isn't available.
\end{itemize}
\newpage
